---
title: "draw_wordcloud"
author: "Tu hao wei"
date: "2018/10/10"
output: html_document
---
I want to find out which champion in League of Legends are difficult to be balanced.
I have an idea. The more frequently it appears in patches, the more difficult to be balanced.
Therefore, I do this program.

#1. Got patch data from LOL website
Function to get content on website about data
```{r setup, include=FALSE}
rm(list=ls(all.names = TRUE))

library(tmcn)
library(rvest)
LOLTestFunction <- function(URL, filename)
{
  html  = read_html(URL)
  
  #ref: https://rpubs.com/SatoshiLiang/159348
  #'.' stands for class, '#' stands for id
  title = html_nodes(html, ".default-2-3 a")
  href  = html_attr(title, "href")
  data = data.frame(title = html_text(title),
                    href = href)
  getContent <- function(x) {
    url  = paste0("https://na.leagueoflegends.com", x)
    tag  = html_node(read_html(url), 'div#patch-notes-container')
    text = html_text(tag)
  }
  allText = sapply(data$href, getContent)
  allText
  write.table(allText, filename) 
}
```

Get first 11 pages of patch notes, and save them
```{r}
id = c(0:10)
URL = paste0("https://na.leagueoflegends.com/en/news/game-updates/patch?page=", id)
filename = paste0(id, ".txt")
mapply(LOLTestFunction, 
       URL = URL, filename = filename)
```

#2. Draw wordcloud
Get the patch data from txt
```{r}
library(NLP)
library(tm)
library(jiebaRD)
library(jiebaR)
library(RColorBrewer)
library(wordcloud)
filenames <- list.files(getwd(), pattern="*.txt")
files <- lapply(filenames, readLines)
docs <- Corpus(VectorSource(files))
```

stem the text
```{r}
toSpace <- content_transformer(function(x, pattern) {
  return (gsub(pattern, " ", x))}
)
docs <- tm_map(docs, removeNumbers)
docs <- tm_map(docs, stripWhitespace)
docs <- tm_map(docs, removeWords, stopwords("english"))
```

Manipulate names of champions
```{r}
champion.name <- read.csv("champion_name/champion_name_3.csv")
str(champion.name)
#because the type of champion.name$Name is numeric, turn it into char
champion.name$Name <- as.character(champion.name$Name)
```

Generate a matrix of word frequency(name frequencey)
```{r}

dtm <- TermDocumentMatrix(docs, control = list(tolower = FALSE))
m <- as.matrix(dtm)
v <- sort(rowSums(m),decreasing=TRUE)
d <- data.frame(word = names(v),freq=v)
selected <- d$word %in% champion.name$Name
nameFreq <- cbind.data.frame(Name = d$word[selected], Freq = d$freq[selected] )

```

Draw the wordcloud
```{r}
par(family=("Heiti TC Light"))
#ref: https://ithelp.ithome.com.tw/articles/10192052
wordcloud(words = nameFreq$Name, freq = nameFreq$Freq,
          scale=c(1,0.1),min.freq=0,max.words=10000,
          random.order=TRUE, random.color=FALSE, 
          rot.per=.1, colors=brewer.pal(8, "Dark2"),
          ordered.colors=FALSE,use.r.layout=FALSE,
          fixed.asp=TRUE)
```

It seems that Rengar, Kindred, Azir are difficult to be balanced